# Chapter 6 (Time Series Decompositon) 

## Question 1
Show that a 3×5 MA is equivalent to a 7-term weighted moving average with weights of 0.067, 0.133, 0.200, 0.200, 0.200, 0.133, and 0.067.

# Centered moving averages can be smoothed by another moving average. This creates a double moving average. In the case of a 3x5 moving average, this signifies a 3 moving average of a 5 moving average. 

# Weights = c(0.067, 0.133, 0.200, 0.200, 0.200, 0.133, 0.067)

# 3x5 MA = [((Y1 + Y2 + Y3 + Y4 + Y5)/5) + ((Y2 + Y3 + Y4 + Y5 + Y6)/5) + ((Y3 + Y4 + Y5 + Y6 + Y7)/5)] / 3

#Plugging in these values proves that the 3x5 moving average is equal to a 7-term weighted moving average

## Question 2
The plastics data set consists of the monthly sales (in thousands) of product A for a plastics manufacturer for five years.

`#` Question 2 (a)
Plot the time series of sales of product A. Can you identify seasonal fluctuations and/or a trend-cycle?
```{r  }
autoplot(plastics)
```

The  data plot shows that there are seasonal fluctuations and there are some upward trend in the plot.


`#` Question 2 (b)
Use a classical multiplicative decomposition to calculate the trend-cycle and seasonal indices
```{r }
decompose.plastics <- plastics %>% decompose(type="multiplicative",  series="Trend") %>%
  autoplot() + xlab("Year") +
  ggtitle("Monthly sales of Product A")

decompose.plastics
```
`#` Question 2 (c)
Yes , the results support the graphical interpretation from part a , we can see seasonal positive trends in the data  

`#` Question 2 (d)
Compute and plot the seasonally adjusted data.
```{r }
autoplot(plastics, main="Monthly sales of Product A", ylab="Sales (Thousands)", xlab="Year") + autolayer(snaive(plastics, h=30), series="Seasonal Naïve", PI=FALSE) + autolayer(naive(plastics, h=30), series="Naïve", PI=FALSE) + autolayer(rwf(plastics, h=30), series="Drift", PI=FALSE)
```

`#` Question 2 (e)
```{r  }
plastics_new <- plastics
plastics_new[20] <- plastics_new[20] + 500
decompose_plastics_new <- decompose(plastics_new, type = "multiplicative"
                                    )
autoplot(plastics_new, series = "Data") +
  autolayer(trendcycle(decompose_plastics_new), 
            series = "Trend") +
  
  autolayer(seasadj(decompose_plastics_new),
            series = "Seasonally Adjusted") +
  xlab("Year") + 
  ylab(" Sales amount per month") +
  ggtitle("Sales of plastic projuct with outlier") +
  scale_color_manual(values=c("gray", "blue", "red"),
                     breaks=c("Data", "Seasonally Adjusted", "Trend"))
```
The outlier has small effect in the trend but also it has huge effect in the adjusted data

`#` Question 2 (F)
Does it make any difference if the outlier is near the end rather than in the middle of the time series?
```{r  }
plastics_new[55] <- plastics_new[55] + 500
decompose_plastics_new <- decompose(
  plastics_new,
  type = "multiplicative"
  )
autoplot(plastics_new, series = "Data") +
  autolayer(trendcycle(decompose_plastics_new),
            series = "Trend") +
  autolayer(seasadj(decompose_plastics_new),
            series = "Seasonally Adjusted") +
  xlab("Year") + ylab("Monthly Sales amount") +
  ggtitle("Sales of plastic projuct with outliers") +
  scale_color_manual(values=c("gray", "blue", "red"),
                     breaks=c("Data", "Seasonally Adjusted", "Trend"))
```
the effect to trend decreases when the outlier been more closer to the end in the plot. 

## Question 3
Recall your retail time series data (from Exercise 3 in Section 2.10). Decompose the series using X11. Does it reveal any outliers, or unusual features that you had not noticed previously?
```{r  }
library(seasonal)
library(readr)
tute1 <- read_csv("C:/Users/baaba/Downloads/tute1.csv")

ts.retail <- ts(tute1[,"Sales"], 
                frequency=12, 
                start=c(1982,4))


autoplot(ts_retail)

retailx11 <- seas(ts.retail, x11="")

autoplot(retailx11, main=" Decomposition on Monthly Retail Sales", xlab="Year")
```

There are some big outliers especially the huge one around 1987 and at the end of 1989

## Question 4
Figures 6.16 and 6.17 show the result of decomposing the number of persons in the civilian labour force in Australia each month from February 1978 to August 1995.

`#` Question 4 (a)
Write about 3–5 sentences describing the results of the decomposition. Pay particular attention to the scales of the graphs in making your interpretation.

The Seasonality chart shows solid seasonal trends in consecutively. The secon chart was interesting where we can we can observe a large increase in July and a significant decrease in March.

`#` Question 4 (b)
Is the recession of 1991/1992 visible in the estimated components?


There are highly change in these data period , if these data was estimated usually it will follow the other data and is will appear more smoother than what we see.

## Question 5
This exercise uses the cangas data (monthly Canadian gas production in billions of cubic metres, January 1960 – February 2005).

`#` Question 5 (a)
Plot the data using autoplot(), ggsubseriesplot() and ggseasonplot() to look at the effect of the changing seasonality over time. What do you think is causing it to change so much?
```{r }
autoplot(cangas, main="Monthly Gas Production", ylab="Gas Production", xlab="Year")

ggsubseriesplot(cangas, main="Monthly Gas Production", ylab="Gas Production")

ggseasonplot(cangas, main="Seasonal Plot: Monthly Gas Production", ylab="Gas Production")
```
When we look at the oil production , we can see that the demand increases closer to the winter months , and that could due to the high use of heating.


`#` Question 5 (b)
Do an STL decomposition of the data. You will need to choose s.window to allow for the changing shape of the seasonal component.
```{r  }
stl_cangas <- stl(cangas, s.window = 13, 
                  robust = TRUE)
# Show each STL decomposed component
autoplot(stl_cangas) 

```
We can see that the seasonality increased in 1980s but it decreases after that in in 1990s 

## Question 6

`#` Question 6 (a)
Use an STL decomposition to calculate the trend-cycle and seasonal indices. (Experiment with having fixed or changing seasonality.)

```{r  }
#fixed seasonality
stl.fixed.st <- stl(bricksq, 
                          s.window = "periodic",
                          robust = TRUE)
autoplot(stl.fixed.st) +
  ggtitle("production data decomposed with fixed seasonality")

#  changing seasonality
stl.changing.st <- stl(bricksq,
                             s.window = 5,
                             robust = TRUE)

autoplot(stl.changing.st) +
  ggtitle(" production data decomposed with changing seasonality")
```

`#` Question 6 (b)
Compute and plot the seasonally adjusted data.

```{r  }
autoplot(bricksq, series = "Data") +
  autolayer(trendcycle(stl.fixed.st),
            series = "Trend-cycle") +
  autolayer(seasadj(stl.fixed.st),
            series = "Seasonally Adjusted Data") +
  ggtitle("Quarterly clay brick production in Australia",
          subtitle = "-decomposed by STL with fixed seasonality") +
  scale_color_manual(values = c("gray", "red", "blue"),
                     breaks = c("Data", "Trend-cycle", "Seasonally Adjusted Data"))
# plot data which are decomposed  with changing seasonality
autoplot(bricksq, series = "Data") +
  autolayer(trendcycle(stl.changing.st),
            series = "Trend-cycle") +
  autolayer(seasadj(stl.changing.st),
            series = "Seasonally Adjusted Data") +
  ggtitle("Quarterly clay brick production in Australia",
          subtitle = "-decomposed by STL with changing seasonality") +
  scale_color_manual(values = c("gray", "red", "blue"),
                     breaks = c("Data", "Trend-cycle", "Seasonally Adjusted Data"))
```

`#` Question 6 (c)
Use a naïve method to produce forecasts of the seasonally adjusted data.
ction", xlab="Year")+ autolayer(naive(bricksq, h=30), series="Naïve", PI=FALSE)


```{r }
stl.fixed.st %>% seasadj() %>% naive() %>% autoplot() + 
  ggtitle(label = "Naive forecast of seasonally adjusted brick data",
          subtitle = "after STL decomposition with fixed seasonality")
stl.changing.st %>% seasadj() %>% naive() %>% autoplot() + 
  ggtitle(label = "Naive forecast of seasonally adjusted brick data",
          subtitle = "after STL decomposition with changing seasonality")
```
The range of the decomposed  with changing seasonalit alsmost similer to the decomposed  with fixed seasonality.

`#` Question 6 (d)
Use stlf() to reseasonalise the results, giving forecasts for the original data.
```{r  }
brick.t <- stlf(bricksq)
brick.t
autoplot(brick.t)
```

`#` Question 6 (e)
Do the residuals look uncorrelated?
```{r }
checkresiduals(brick.t)
```
residuals are correlated with each other 

`#` Question 6 (f)
Repeat with a robust STL decomposition. Does it make much difference?
```{r  }
brick.tt <-  stlf(bricksq, robust = TRUE)
autoplot(brick.tt)
checkresiduals(brick.tt)
```
We can see there are still correlation  even with the robust


`#` Question 6 (g)
Compare forecasts from`stlf()`with those from`snaive()`,using a test set comprising the last 2 years of data. Which is better?
```{r  }
trainset.brick <- subset(bricksq, 
                        end = length(bricksq) - 8)
testset.brick <- subset(bricksq,
                        start = length(bricksq) - 7)
snaive.brick <- snaive(trainset.brick)
stlf.brick <- stlf(trainset.brick, robust = TRUE)


snaive_brick
stlf.brick
```

```{r  }
autoplot(bricksq, series = "Original data") +
  geom_line(size = 1) +
  autolayer(stlf_brick_part, PI = FALSE, size = 1,
            series = "stlf") +
  autolayer(snaive_brick, PI = FALSE, size = 1,
            series = "snaive") +
  scale_color_manual(values = c("gray50", "blue", "red"),
                     breaks = c("Original data", "stlf", "snaive")) +
  scale_x_continuous(limits = c(1990, 1994.5)) +
  scale_y_continuous(limits = c(300, 600)) +
  guides(colour = guide_legend(title = "Data")) +
  ggtitle("Forecast stlf and snaive functions") +
  annotate(
    "rect",
    xmin=1992.75,xmax=1994.5,ymin=-Inf,ymax=Inf,
    fill="lightgreen",alpha = 0.3
    )
```

## Question 7
Use`stlf()`to produce forecasts of the`writing`series with either`method="naive"`or`method="rwdrift"`,whichever is most appropriate. Use the`lambda`argument if you think a Box-Cox transformation is required.

I think is it would be better to use`rwdrift`method to forecast non-seasonal component
```{r  }

writingBC <- stlf(writing, 
                  method='rwdrift', 
                  robust=TRUE, 
                  lambda = BoxCox.lambda(writing)
                  
                  )
autoplot(writingBC)
```

## Question 8
Use`stlf()`to produce forecasts of the`fancy`series with either`method="naive"`or`method="rwdrift"`,whichever is most appropriate. Use the`lambda`argument if you think a Box-Cox transformation is required.

```{r  }
stlf.fancy <- stlf(fancy,
                   robust = TRUE,
                   lambda = BoxCox.lambda(fancy),
                   method = "rwdrift")
autoplot(stlf.fancy)
```
because of the Box-Cox transformation the intervals increase increases highly 


